Lobbying and Legislative Uncertainty

### 2016-05-09 presentation.tex

\title[Lobbying and Legislative Uncertainty\hspace{2.95in}\insertframenumber/\inserttotalframenumber]{Lobbying and Legislative Uncertainty}
%\author[Kristy Buzard]{Kristy Buzard \\ Syracuse University and The Wallis Institute \\ kbuzard@syr.edu}
\author[Kristy Buzard]{\texorpdfstring{Kristy Buzard\newline Syracuse University and The Wallis Institute  \newline\url{kbuzard@syr.edu}}{Kristy Buzard}}
\date{May 10, 2016}
\begin{document}
\maketitle
%\insertpresentationendpage removed b/c of appendix

@@

\begin{frame}{Vote Buyer B's Objective Function}
\pause
Let $X(i) = 1$ denote legislator $i$ votes for the status quo
\pause
\begin{multline*}
			    \max_{b_{-.5}, b_0, b_{.5}} 
					W_B \biggl[ \Pr\left(X\left(-.5\right)=1\right)\Pr\left(X\left(0\right)=1\right)\left(X\left(.5\right)=0\right)  + \\
					\Pr\left(X\left(-.5\right)=1\right)\Pr\left(X\left(0\right)=0\right)\Pr\left(X\left(.5\right)=1\right) + \\
					\Pr\left(X\left(-.5\right)=0\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(.5\right)=1\right) + \\
					\Pr\left(X\left(-.5\right)=1\right)\Pr\left(X\left(0\right)=1\right)\Pr\left(X\left(.5\right)=1\right) \biggr] - \sum_{j\in \left\{-.5, 0,.5\right\}} b_j
				\end{multline*}
\end{frame}

>>>>

\title[Lobbying and Legislative Uncertainty\hspace{2.95in}\insertframenumber/\inserttotalframenumber]{Lobbying and Legislative Uncertainty}
\author[Buzard and Saiegh \hspace{2.7in} \url{kbuzard@syr.edu}]{Kristy Buzard \inst{1} \and Sebastian Saiegh \inst{2}}
\institute{\inst{1} Syracuse University and The Wallis Institute \and \inst{2} UC San Diego}
\date{May 10, 2016}
\begin{document}
\maketitle
%\insertpresentationendpage removed b/c of appendix

@@

\begin{frame}{Vote Buyer B's Objective Function}
\pause
Let $S(i) = 1$ denote legislator $i$ votes for the status quo
\pause
\begin{multline*}
			    \max_{b_{-.5}, b_0, b_{.5}} 
					W_B \biggl[ \Pr\left(S\left(-.5\right)=1\right)\Pr\left(S\left(0\right)=1\right)\left(S\left(.5\right)=0\right)  + \\
					\Pr\left(S\left(-.5\right)=1\right)\Pr\left(S\left(0\right)=0\right)\Pr\left(S\left(.5\right)=1\right) + \\
					\Pr\left(S\left(-.5\right)=0\right)\Pr\left(S\left(0\right)=1\right)\Pr\left(S\left(.5\right)=1\right) + \\
					\Pr\left(S\left(-.5\right)=1\right)\Pr\left(S\left(0\right)=1\right)\Pr\left(S\left(.5\right)=1\right) \biggr] - \sum_{j\in \left\{-.5, 0,.5\right\}} b_j
				\end{multline*}
\end{frame}
